Visualizations for the manuscript

### 2022-03-15 metanalysis_visualization/manuscript_Figures.Rmd
updating length of stay and bootstrap

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                         mental_codes_qc_output %>%
                                           select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    )
    table1_all <- rbind( table1_all, table1)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
    rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
       bootstrapped_fitted_df, mental_codes_qc_output, table1)
  }
}

@@

@@

table1 <- rbind( sex_table1_all, age_table1_all, dg_table1_all )

@@

@@

```{r}

quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

@@

plot_annotations <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

>>>>

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    length_hospitalisation_values_all <- length_hospitalisation_values
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                         mental_codes_qc_output %>%
                                           select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    )
    table1_all <- rbind( table1_all, table1)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
    length_hospitalisation_values_all <- tryCatch(
      rbind(length_hospitalisation_values_all, length_hospitalisation_values),
      error = function(e) length_hospitalisation_values_all
    )
    rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
       bootstrapped_fitted_df, mental_codes_qc_output, table1, length_hospitalisation_values)
  }
}

@@

```{r}
median_table1_all <- length_hospitalisation_values_all %>% 
  filter(siteid != "CCHMC") %>% # temporary
  group_by(period) %>% 
  summarise(median_hospitalisation = median(len_hospitalisation)) %>% 
  pivot_wider(names_from = period, values_from = median_hospitalisation) %>% 
  mutate(Category = "Length of stays", 
         name = "median") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
```

@@

table1 <- rbind( sex_table1_all, age_table1_all, median_table1_all, dg_table1_all )

@@

## Recompute the bootstrap

```{r}
# Call function from another file : bootstrap.R
bootstrap_size <- 1000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

bootstrapping_slopes <- function(patient_count_psy_period_psy, 
                                    bootstrap_size) {
  bootstrapped_timepoints <- mapply(binom_proportion,
                                    n = bootstrap_size,
                                    size = patient_count_psy_period_psy$count_no_psy_patients +
                                      patient_count_psy_period_psy$count_psy_patients,
                                    prob = patient_count_psy_period_psy$percentage/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                               time = patient_count_psy_period_psy$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- patient_count_psy_period_psy$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration")
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration")
  return(list(bootstrapped_coefficients_df, 
              bootstrapped_fitted_df))
}

# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ... 
count_icd_all_boot <- count_icd_all %>% 
  group_by(siteid) %>% # necessary to generate time correctly 
  rename(count_psy_patients = count_psy, 
         percentage = percentage_psy) %>% 
  mutate(count_no_psy_patients = count_icd - count_psy_patients, 
         month_year = format(time_p, "%m"),
         time = seq_along(time_p))

bootstrapped <- count_icd_all %>% 
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size))
names(test) <- unique(count_icd_all$siteid)

bootstrapped_coefficients_all <- lapply(bootstrapped, `[[`, 1) %>% bind_rows(.id = "siteid")
bootstrapped_fitted_all <- lapply(bootstrapped, `[[`, 2) %>% bind_rows(.id = "siteid")
```

@@

```{r}
quantile_bootstrapped_fitted_all <- bootstrapped_fitted_all %>%
  group_by(time_p, period, siteid) %>%
  summarise("2.5%" = quantile(predicted, 0.025),
            "50%" = median(predicted, 0.5),
            "97.5%" = quantile(predicted, 0.975)) %>%
  pivot_longer(cols = c("2.5%", "50%", "97.5%"),
               names_to = "quantiles")

@@

plot_annotations <- df_coefficients_boot %>% 
  group_by(siteid) %>% 
  group_map( annotation_function ) %>% 
  set_names(names_site_id) %>% 
  unlist()
plot_annotations_df <- data.frame(
  siteid = names(plot_annotations), 
  label = plot_annotations
)
```

```{r}
### January 19-May 21
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = count_icd_all_boot,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all_extended.png", height = 20, width = 32, units = "cm")
```

```{r}
### Feb 19-April 21
ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```
